Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change

### 2024-07-02 ms.qmd
Added some more code to pool chains and wrote results on LH for lnRRQ10

# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution

    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.

        # Contrast statistics
            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
                                                     stage = rep(c("j", "a"), each = 1),
                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))

    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.

        # Contrast statistics
            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
                                                     tyoe = rep(c("acute", "acclim"), each = 1),
                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
  ######## OLD CODE BELOW>
        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species

    # Freshwater
        f_ad <- 4
        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species

    # Terrestrial
        t_ad <- 8
        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species

# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
         m_acute_lh <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
        m_acclim_lh <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species

    # Freshwater
            f_ad <- 4
         f_acute_lh <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
        f_acclim_lh <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species

    # Terrestrial
            t_ad <- 8
         t_acute_lh <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
        t_acclim_lh <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species

  # Acute differences between a and j across all habitats
     acute_all_lh <- c(m_acute_lh, f_acute_lh, t_acute_lh); mean(acute_all_lh); quantile(acute_all_lh, c(0.025, 0.975)); pmcmc(acute_all_lh)
    acclim_all_lh <- c(m_acclim_lh, f_acclim_lh, t_acclim_lh)

# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong. These two lines of code should roughly match
#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")

@@

Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).

>>>>

# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
  ############
    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
  ############
  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.

        # Contrast statistics
            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
                                                     stage = rep(c("j", "a"), each = 1),
                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
    ############
    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
    ############
          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.

        # Contrast statistics
            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
                                                     type = rep(c("acute", "acclim"), each = 1),
                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))

  # Acute differences between a and j across all habitats
     acute_all_lh <- c(contrast_lnrr_lh_post_type[1,], contrast_lnrr_lh_post_type[3,], contrast_lnrr_lh_post_type[5,]) 
    acclim_all_lh <- c(contrast_lnrr_lh_post_type[2,], contrast_lnrr_lh_post_type[4,], contrast_lnrr_lh_post_type[6,])

@@

Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles (@fig-cvrlh A-C). When comparing between acute and acclimation responses between adults and juveniles there were also no differences across habitats (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
